### 2021-08-07 README.Rmd
Minor edits to references and readme
Added link to pre-print and osf repository

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Exploring the composition of lithic assemblages in Mesolithic
south-eastern Norway"
```

@@

>  Roalkvam, Isak (2021). *`r Title`*. Accessed
> `r format(Sys.Date(), "%d %b %Y")`. Online at
> <https://doi.org/xxx/xxx>

@@

> Roalkvam, Isak (`r format(Sys.Date(), "%Y")`). *Compendium of R code and
> data for `r Title`*. Accessed `r format(Sys.Date(), "%d %b %Y")`.
> Online at <https://doi.org/xxx/xxx>

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Exploring the Composition of Lithic Assemblages in Mesolithic South-Eastern Norway"
```

@@

>  Roalkvam, Isak (2021). *`r Title`*. Accessed
> `r format(Sys.Date(), "%d %b %Y")`. Online at
> <https://doi.org/10.31235/osf.io/cqaps>

@@

> Roalkvam, Isak (`r format(Sys.Date(), "%Y")`). *Compendium of R code and
> data for `r Title`*. Accessed `r format(Sys.Date(), "%d %b %Y")`.
> Online at <https://doi.org/10.17605/osf.io/ehjfc>
